SDM\_the\_search\_for\_powers\_of\_2\_everywhere

### 2018-04-27 Chapters/sdm2.tex
The incredible animal behavior of Dr Linhares

The space studied by Kanerva is also called the \emph{hypercube graph}, or $Q_n$, as in Figure \ref{hypercubes}. For a fixed $n \in \mathbb{Z}$, the graph $G = (V, E)$, in which $v \in V$ iff there is a bijective function $b: V\to \{0,1\}^n$ and $(v_i, v_j) \in E$ iff $H(b(v_i), b(v_j))=1$, where $H$ is the Hamming distance. That is, $n$-sized bitstrings correspond to nodes, and edges exist between nodes $iff$ they flip a single bit.  Though Kanerva has derived many combinatorial properties of the space, additional results have been found by the graph-theoretical community. A good survey is provided by \citet{harary1988survey}.

@@

It is important to say that Chada's read came from \citet{anwar2003sparse} which gave a misguided description of the read operation. The original description is the following:

\begin{samepage}
\begin{quote}
%Similar to writing, retrieving from SDM involves the same concept of access sphere --- you read all the hardlocations within the access sphere of location Y, pool the bit vectors read from all these hard locations and let each of the kth bits of those locations participate in a majority vote for the kth bit of Y. \hfill --- \citet{anwar2003sparse}
With our datum distributively stored, the next question is how to retrieve it. With this in mind, let us ask first how one reads from a single hard location, $x$. Compute $\zeta$, the bit vector read at $x$, by assigning its $i$th bit the value 1 or 0 according to the $i$th counter at $x$ is positive or negative. Thus, each bit of $\zeta$ results from a majority rule decision of all the data that have been written at $x$. [...] Knowing how to read from a hard location allows us to read from any of the $2^{1000}$ arbitrary locations. Suppose $\zeta$ is any location. The bit vector, $\xi$, to be read at $\zeta$, [...] Put another way, pool the bit vectors read from hard locations accessible from $\zeta$, and let each of their $i$th bits vote on the $i$th bit of $\xi$. \\
\hfill --- \citet[p.342]{anwar2003sparse}
\end{quote}
\end{samepage}

>>>>

The space studied by Kanerva is also called the \emph{hypercube graph}, or $Q_n$, as in Figure \ref{hypercubes}. For a fixed $n \in \mathbb{Z}$, the graph $G = (V, E)$, in which $v \in V$ iff there is a bijective function $b: V\to \{0,1\}^n$ and $(v_i, v_j) \in E$ iff $H(b(v_i), b(v_j))=1$, where $H$ is the Hamming distance. That is, $n$-sized bitstrings correspond to nodes, and edges exist between nodes $iff$ they flip a single bit.  Though Kanerva has derived many combinatorial properties of the space, additional results have been found by the graph-theoretical community. A good survey is provided by \citet{harary1988survey} --- and some interesting results may be found in \citep{foldes_characterization_1977, wagner_embedding_1990, laborde_another_1982, ruskey_combinatorial_2003}.

@@

It is important to say that Chada's read came from \citet{Anwar2003} which gave a misguided description of the read operation. The original description is the following:

\begin{samepage}
\begin{quote}
%Similar to writing, retrieving from SDM involves the same concept of access sphere --- you read all the hardlocations within the access sphere of location Y, pool the bit vectors read from all these hard locations and let each of the kth bits of those locations participate in a majority vote for the kth bit of Y. \hfill --- \citet{Anwar2003}
With our datum distributively stored, the next question is how to retrieve it. With this in mind, let us ask first how one reads from a single hard location, $x$. Compute $\zeta$, the bit vector read at $x$, by assigning its $i$th bit the value 1 or 0 according to the $i$th counter at $x$ is positive or negative. Thus, each bit of $\zeta$ results from a majority rule decision of all the data that have been written at $x$. [...] Knowing how to read from a hard location allows us to read from any of the $2^{1000}$ arbitrary locations. Suppose $\zeta$ is any location. The bit vector, $\xi$, to be read at $\zeta$, [...] Put another way, pool the bit vectors read from hard locations accessible from $\zeta$, and let each of their $i$th bits vote on the $i$th bit of $\xi$. \\
\hfill --- \citet[p.342]{Anwar2003}
\end{quote}
\end{samepage}
